DDSAnalytics  - Employee Trends

### 2018-04-10 msds6371-group-project-kaggle.Rmd
Edit doc, add table and more sections'

This is the final project for the semester in MSDS 6371 Statistical Foundation for Data Science, and is a group project.  It is based on the [Kaggle House Prices competition](https://www.kaggle.com/c/house-prices-advanced-regression-techniques).  Fundamentally we are seeking to answer: based on some combination of predictive attribute measures of a housem how much will the final sale price be.  The 2 specific questions prescribe to distinct approaches to answering this question.

@@

This dataset, is roughly 441k with 1459 observation of 80 variables.  This has one less observation: SalesPrices.  This is due to the fact it is meant to be used for cross-validation, and does not require this variable.

@@

Provide for Century 21 Ames real estate the following analysis of homes:

@@

### Assumptions

@@

##### Assumptions

### Comparison of Models

>>>>

This is the final project for the semester in MSDS 6371 Statistical Foundation for Data Science, and is a group project.  It is based on the [Kaggle House Prices competition](https://www.kaggle.com/c/house-prices-advanced-regression-techniques).  Fundamentally we are seeking to answer what will the sale price of a house be based on some combination of predictive attribute measures of it.  The 2 specific questions below prescribe distinct approaches to answering this question.

@@

This dataset, is roughly 441k with 1459 observation of 80 variables.  This has one less observation: SalesPrices.  This is due to the fact it is meant to be used for cross-validation, and does not require this variable because we are meant to predict that with our models.

@@

Ames Century 21 real estate would like us to perform the following analysis of homes:

@@

### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

@@

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

#### Backward

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

#### Stepwise

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

#### Custom

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

### Comparison of Models
| Predictive Models | Adusted R^2 | CV Press | Kaggle Score |
|-------------------|:-----------:|:--------:|:------------:|
| Forward           | 0.1111      | 1111     | .111         |
| Backward          | 0.2222      | 2222     | .222         |
| Stepwise          | 0.3333      | 3333     | .333         |
| Custom            | 0.4444      | 4444     | .444         |
